Variance reduction for MCMC methods via martingale representations

### 2020-04-10 aap/Revision/vr-mcmc-revision-new-new.tex
update

@@

\PVar_{0} \pi_n^0(f) &=& \PVar_{0}\left[\frac{1}{n}\sum\limits_{i=1}^{n}X_i\right] 

@@

One of the main results of this paper is the following  upper bound for the functions $(A_{q,\mathbf{k}}).$

@@

where $F_q(x,Z_1,\ldots,Z_q)=\sum_{r=0}^q f(X^x_r)$ and $\partial_{Z_1}^{\mathbf{k}'}$

@@

Also from \eqref{eq:Ask-part} we can derive

@@

Finally, we show  that under our smoothness assumption \eqref{eq:smooth-mu} it holds

@@

First we note that from  numerical point of view another representation of the coefficients \(a_{p,l,k}\)  turns out to be more useful.

@@

 We construct a polynomial approximation  for each \(Q_r(x)\) in \eqref{eq:definition-bar-a} in the form:

>>>>

\label{eq:A-ula}

@@

\PVar_{0} [\pi_n^0(f)] &=& \PVar_{0}\left[\frac{1}{n}\sum\limits_{i=1}^{n}X_i\right] 

@@

One of the main results of this paper is the following  upper bound for the functions $(A_{q,\mathbf{k}})$ in \eqref{eq:A-ula}.

@@

where $F_q(x,Z_1,\ldots,Z_q):=\sum_{r=0}^q f(X^x_r)$ and $\partial_{Z_1}^{\mathbf{k}'}$

@@

Also from \eqref{eq:Ask-part} we can derive that

@@

Finally, using the Gaussian Poincare inequality, we show  that under our smoothness assumption \eqref{eq:smooth-mu} it holds

@@

First we note that from  numerical point of view another equivalent representation of the coefficients \(a_{p,l,k}\)  turns out to be more useful.

@@

First we construct a polynomial approximation  for each \(Q_r(x)\)  in the form:
